Despite the attractive features of the ME method and promise of
further optimization and parallelization of the evaluation of
Eqn.~\ref{eqn:MEProb}, the computational burden of the ME technique
will continue to limit is range of applicability for practical data
analysis without new and innovative approaches. This is especially
true when one considers the process of producing a physics publication
which involves many selection, sample and systematic iterations for
which ME calculations are required. The primary idea put forward in
this Section is to utilize modern \emph{machine learning techniques to
dramatically speed up the numerical evaluation of
Eqn.~\ref{eqn:MEProb}} and therefore broaden the applicability of the
ME method to the benefit of the HL-LHC physics program.

Applying neural networks to numerical integration problems is
plausible but not new
(see~\cite{CSEarticle2006,TICNC4344207,IJMC2013}, for example). The
technical challenge is to design a network which is sufficiently rich
to encode the complexity of the ME calculation for a given process
over the phase space relevant to the signal process. Deep Neural
Networks (DNNs) are stong candidates for networks with sufficient
complexity to achieve good approximation of Eqn.~\ref{eqn:MEProb},
possibly in conjunction with smart phase-space mapping such as
described in~\cite{Artoisenet:2010cn}. Promising demonstration of the
power of Boosted Decision Trees~\cite{friedman2000,friedman2001} and
Generative Adversarial Neural Networks~\cite{GAN2014arXiv1406.2661G}
for improved Monte Carlo integration can be found
in~\cite{Bendavid:2017zhk}. Once a set of DNNs representing of
definite integrals of the form of Eqn.~\ref{eqn:MEProb} to good
approximation are generated, evaluation of the ME method calculations
via the DNNs will be very fast. These DNNs can be throught of as
preserving the essence of ME calculations in a way that allows for
fast forward execution. The net result is that the DNNs can enable the
ME method to be both \emph{nimble} and \emph{sustainable}, neither of
which is true today.
